Machine Learning Methods in Functional Programming and Interactive Theorem Proving

### 2015-10-29 TransferReport/report.tex
Rename overlapping key

We can divide AC approaches into two groups: the first, which we call \emph{explicit}, send inputs which follow a Wundt curve to their learning algorithm; the second, the \emph{implicit} approaches, instead modify the \emph{output} of their learning algorithm, such that the behaviour follows a Wundt curve.

>>>>

We can divide AC approaches into two groups: the first, which we call \emph{explicit}, send inputs which follow a Wundt curve to their learning algorithm; the second, the \emph{implicit} approaches, instead modify the \emph{output} of their learning algorithm(s), such that the overall system still follows a Wundt curve as an emergent property.
